---
title: "PGx_annotated"
author: "Sam"
date: "September 19, 2019"
output: 
  pdf_document:
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

#packages required 
packages + function need to run the code in this file
```{r load packages}
library(data.table)
library(tidyverse)
library(plyr)
library(reshape2)
library(compare)
library(rowr)

#renames column based on column index not name 
rename_col_by_position <- function(df, position, new_name) {
  new_name <- enquo(new_name)
  new_name <- quo_name(new_name)
  select(df, !! new_name := !! quo(names(df)[[position]]), everything())
}
```

# load data
### loading in and tiding all inital data sets
### output files:
* tidy_mydna.csv = tidy myDNA genotype data
* tidykailos.csv = tidy kailos genotype data
* allmydrugdata.csv = tidy myDNA drug/phenotype data

```{r load data}

#change working directory to that with myDNA CSVs
setwd("C:/Users/Sam/Documents/pgx/mydna")

#load in snp data and genotype data: rename some columns to match those in mydna CSVs
snpdat<-read.csv("C:/Users/Sam/Documents/pgx/mydna snps - Sheet1.csv")
mydata<-read.csv("C:/Users/Sam/Documents/pgx/mygenotypes.csv")%>%
  rename(c('gene' = 'GENE', 'genotype' = 'GENOTYPE'))
  

#load in and bind all myDNA genotype CSVs into one file.
#remove trailing spaces
files <- list.files()
temp <- lapply(files, fread, sep=",")
data <- rbindlist(temp)%>%
  mutate_if(is.character, str_trim)

#make CSV of all myDNA patient genotype information
write_csv (data, "C:/Users/Sam/Documents/pgx/results/tidy_mydna.csv")

#load in kailos data and remove any trailing spaces
kdata<-read.csv("C:/Users/Sam/Documents/pgx/allkailos4.csv")

kd<-kdata %>% mutate_if(is.factor, as.character)%>%
  mutate_if(is.character, str_trim)

# tidy data: create gene column, replace nulls with NA and then remove na rows, rename columns to match 
m<-melt(kd, id.vars = "ID", measure.vars = 2:39)%>%
  mutate_all(~replace(., . == "", NA)) %>%
  na.omit()%>%
  rename(c('variable' = 'GENE', 'value'='kailos_call'))

#output tidy data as a cSV
write.csv(m, "C:/Users/Sam/Documents/pgx/results/tidykailos.csv")

#load in my DNA patient drug response data, bind into one data frame and remove any trailing spaces
setwd("C:/Users/SamBr/Documents/pgx/myDNA_drugs_CLEAN2")
files2 <- list.files()
temp2 <- lapply(files2, fread, sep=",")
data2 <- as.data.frame(rbindlist(temp2, use.names = TRUE))%>%
  mutate_if(is.character, str_trim)

#create pharmacy ID column 
sites<-separate(data2,ID, into = c("site", "xxx"), sep = "-", remove = F )%>%
  select(-xxx)

#output tidy data as csv
write.csv(sites, "C:/Users/Sam/documents/pgx/results/allmydrugdata.csv")
```
# Frequency of myDNA calls
### calculating the frequency of myDNA calls
### output files:
* mydna_freq.csv = number of times each myDNA genotype was called

```{r get myDNA freq}
#split dataframe into seperate data frames based on gene 
xx<-split(data, data$GENE, drop = F)

# create function to get genotype frequencies 
genotype_freqs<-function(df){
  v<-table(df$GENOTYPE)%>%
  as.data.frame()%>%
  rename(c('Var1' = 'GENOTYPE'))%>%
  mutate(myDNA_call_freq_percent = Freq/150*100)%>%
  merge(df, by = 'GENOTYPE')}

# get genotype frequncies and bind back into one data frame
data_F<-lapply(xx, genotype_freqs)%>%
  rbindlist()%>%
  rename(c('Freq' = 'myDNA_call_freq'))

# return only unique rows
data_Freq <- data_F%>%
  select(-ID,-`PREDICTED FUNCTION`)%>%
  unique()

#merge with population data
frequencies<-merge(mydata, data_Freq, by = c("GENE","GENOTYPE"))

#round to 2 digits
frequencies<- format(frequencies, digits = 2)

#create csv of mydna gene freqs
write_csv (frequencies, "C:/Users/Sam/Documents/pgx/results/myDNA_freq.csv")
```
# Frequency of kailos calls
### output files:
* kailos_call.csv = number of times all kailos snps were called

```{r get kailos freq}

#get unique kailos genotype frequencies and round table

lol<-table(m$kailos_call)%>%
  as.data.frame()%>%
  rename(c('Var1' = 'kailos_call'))%>%
  mutate('kailos_Genotype_Freqency_%' = Freq/37*100)%>%
  rename(c('Freq' = 'kailos_Genotype_Freqency'))%>%
  merge(m, by = 'kailos_call')%>%
  select(-ID)%>%
  unique()%>%
  format(digits = 2)

#output kailos genotype frequncies as a csv
write.csv(lol, "C:/Users/Sam/Documents/pgx/results/kailos_freq.csv")

# remove rs codes that dont exist in the myDNA data set
toMatch<-c('rs9923231', 'rs762551', 'rs4149056','CYP2D6', 'CYP2C19', 'CYP3A4', 'CYP3A5', 'CYP2C9')
k_calls_only<-filter(m, grepl(paste(toMatch, collapse="|"), kailos_call))

# get frequncy of only those genes that exist in both data sets 
kailosco_freq <-table(k_calls_only$kailos_call)%>%
  as.data.frame()%>%
 rename(c('Var1' = 'kailos_call'))%>%
  mutate('kailos_Genotype_Freqency_%' = Freq/37*100)%>%
  rename(c('Freq' = 'kailos_Genotype_Freqency'))%>%
  merge(m, by = 'kailos_call')%>%
  select(-ID)%>%
  unique()%>%
  format(digits = 2) 

```

# Comparison of my kailos and myDNA genotype calls

#### t60-163 and t60-169 failed mydna genotyping. - passed kailos 
* both were retested and t60-169 passed (t60-163 did not)
* changed sample name in kailos file to t60-169-RT so they could be compared\

#### think L65-294 and L65-295 were swapped and L65-293 = L65-296
* changed names to reflect this in the kailos data file
* L65-293 = L65-296
* L65-294 = L65-295
* L65-295 = L65-294 

#### 35a called only in kailos reports 
* has normal metaboliser status 
* subset of *2 allele (2851 c>t, 4181 g>c VS. 2851 c>t, 4181 g>c AND 31 g>A )

#### output files:
* different_genotype.csv = table of samples whose genotype calls did not match between data sets
* my_vs_kailosgenotypes.csv = comparison of all myDNA and kailos calls 

```{r kailos vs myDNA genotypes}

#introduce patient ids back into genotype freq data
mydata_geno<-merge(mydata, data, by = c("GENE","GENOTYPE"))

#merge in kailos data
my_v_k<-merge( k_calls_only,mydata_geno, by = c("GENE","ID"), all = T) 

#remove myDNA genes that are not found in the kailos data det 
mmm<-my_v_k[!is.na(my_v_k$kailos_call.x),]%>%
  select( -GENOTYPE, -population.level, -phenotype, -'PREDICTED FUNCTION')%>%
  rename(c("kailos_call.x" = 'kailos_call', 'kailos_call.y' = "myDNA_call"))

#create column to hightlight different gene calls between data sets (x = same)
mmm$compare <-ifelse(mmm$kailos == mmm$myDNA,  "x",ifelse(mmm$kailos != mmm$myDNA, "different", "a"))

# create data frame of only differing gene calls
diffrentsamples<-filter(mmm, compare == "different")

#output myDNA v. Kalios comparison table and table of samples that differ between data sets
write.csv(diffrentsamples, "C:/Users/Sam/Documents/pgx/results/different_genotypes.csv")
write.csv(mmm, "C:/Users/Sam/Documents/pgx/results/my_vs_kaliosgenotypes.csv")
```
# myDNA vs kailos genotype freqencies compared with population level 
### genotype frequencies for CYP2D6, CYP2C19, CYP2C9 and VKORC1 
* taken from myDNA paper 
* (doi: 10.1007/s00702-018-1922-0)
* two cyp2d6 alleles tested for(29 and 36) were not mentioned at all in study. one person was found to have a *36 (1/36) genotype
** used frequency from this paper (doi: 10.3389/fphar.2018.00305) and matched to 1/14b genotype which had the same snp freq  

### Genotype frequencies for SLCO1B1, CYP1A2, CYP3A4, CYP3A5, and OPRM1 
* calculated from SNP frequency in hardy winberg equlibrium
* snp frequency found from ncbi.nlm.nih.gov (us national library of medicine snp database) spec frequncy is the global frequency recorded by the genome aggregation database (gnomeAD)

### output files:
* my_vs_kailos_freq_pop = kailos vs my dna genotype frequencies 

```{r myDNA vs kailos genotype freq}
#merge kailos freq into myDNA freq table
mykailos<-join(frequencies, lol, by = "kailos_call", match = "all")

#remove last colunmn (duplicate)
mykailos<-mykailos[c(1:9)]

#output frequency comparison as csv 
write.csv(mykailos, "C:/Users/Sam/Documents/pgx/results/my_vs_kailos_freq_pop.csv")
```

# drug vs phenotype frequencies
### remove/replace warfin columns
  * Normal warfarin sensitivity = Normal metaboliser
  * High warfarin sensitivity = Poor metaboliser
  * Increased warfarin sensitivity = Reduced metaboliser

### output files:
* myFUNCTION_drug_freq.csv = frequncy of each predicted phenotype
* drug_pheno.csv = number of times each phenotype was called for each drug based on gene
```{r drug pheno}
#get unique drug gene information, rename colum to match 
drugs<-sites[c("MEDICATION", "GENE(S)\rINVOLVED")]%>%
  unique()%>%
  rename_col_by_position(2, GENE)

# couldnt get the genes to correctly sepreate into individual rows so outputed data as csv and edited by hand. hashed line so it wouldnt overwrite good drug file
# write.csv(drugs, "C:/Users/Sam/Documents/pgx/drugs.csv")

#read back in good drug file
drugs<-read.csv("C:/Users/Sam/Documents/pgx/drugs.csv")


#get frequency of each perdicted metabolism function
mydrugs<-table(data$`PREDICTED FUNCTION`)%>%
  as.data.frame()%>%
  rename(c('Var1' = 'PREDICTED FUNCTION'))%>%
  mutate(per_fun_freq = Freq/150*100)%>%
  rename(c('Freq'= 'Phenotype_freq'))%>%
  merge(data, by = 'PREDICTED FUNCTION')%>%
  select(-ID, -GENOTYPE)%>%
  unique()

#merge in drug data  
function_freq_drug<-merge(mydrugs, drugs, by ="GENE")

#output frequency of perdicted phenotype/drug table as csv 
write.csv(function_freq_drug, "C:/Users/Sam/Documents/pgx/results/myFUNCTION_drug_freq.csv")

#get cleaner function/ phenotype data
pheno_data<-mydata_geno%>%
  select(phenotype, 'PREDICTED FUNCTION')

#merge in phenotype information and remove trailing spaces
fun_pheno<-merge(function_freq_drug, pheno_data, by = 'PREDICTED FUNCTION' )%>%
  unique()
fun_pheno<-fun_pheno %>% mutate_if(is.factor, as.character)%>%
  mutate_if(is.character, str_trim)

#number of times each drug per gene is impacted by each phenotype
cast_pheno<-dcast(fun_pheno, MEDICATION+GENE~phenotype, fun.aggregate = sum, value.var = "Phenotype_freq")
#output file as csv
write.csv(cast_pheno, "C:/Users/Sam/Documents/pgx/drug_pheno.csv")
```

# number of drug consideration per study site
### output files:
* site_consideration.csv = frequency of each pharmacogentic consideration for each study site and medication 

```{r site drug consideration}
# get frequency of each pharmacogentic consideration for each study site and medication 
conc_freq<-as.data.frame(table(sites$site, sites$CONSIDERATION, sites$MEDICATION))%>%
  rename(c('Var1'= 'site', 'Var2' = 'CONSIDERATION', 'Var3'= 'MEDICATION'))%>%
  merge(sites, by = c('site', 'CONSIDERATION', 'MEDICATION'))%>%
  rename(c('GENE(S)\rINVOLVED'= 'GENEs'))

#cast site column and use frequency column to fill
cast_site<-dcast(conc_freq, MEDICATION+GENEs+CONSIDERATION~site, fun.aggregate = mean, value.var = "Freq")%>%
  rename(c('BCP'= 'BCP (n=8)', "D59"  ='D59 (n=1)', "F31" = 'F31 (n=2)' ,   "J02" = "J02 (n=8)", "K74" = 'k74 (n=6)', "K76" = "k76 (n=10)" ,"L65" = "L65 (n=20)",
           "N24"= "N24 (n=20)" , "N43"= "N43 (n=9)", "N83" = "N83 (n=16)", "S73"= "S73 (n=5)", "S81"= "S81 (n=4)", "S94" = "S94 (n=3)", "T37"= "T37 (n=9)", "T60" = "T60 (n=9)", 
           "W19" = "W19 (n=10)", "X73" = "X73 (n=10)"))

#change NAN values to 0 
cast_site[is.na(cast_site)] <- 0
#output as a csv 
write.csv(cast_site, "C:/Users/Sam/documents/pgx/results/site_consideration.csv")
```

# missing drug 
from here on is me investigating (in a round about way) the missing drug, acenocoumarol, in the three patients J02-131, L65-291, and N24-325

```{r missing drug}
lo<-split(sites, sites$ID)

  
drugcat<-as.data.frame(lo$`BCP-011`$`DRUG CATEGORY`, lo$`BCP-011`$MEDICATION)%>%
  rownames_to_column()%>%
  rename_col_by_position(1, 'MEDICATION')%>%
  rename_col_by_position(2, `DRUG CATEGORY`)

sites<-sites%>%
  select(-'DRUG CATEGORY')%>%
  merge(drugcat)

drugc<-split(sites, sites$`DRUG CATEGORY`)
majorAC<-split(drugc$Anticoagulants, drugc$Anticoagulants$CONSIDERATION)
view(majorAC$major)
med<-split(majorAC$usual, majorAC$usual$MEDICATION)


m<-"drug"
normal<-as.data.frame(lo$`BCP-011`$MEDICATION)%>%
  rename_col_by_position(1, drug)

j02131<-as.data.frame(lo$`J02-131`$MEDICATION)%>%
  rename_col_by_position(1, drug)
l65291<-as.data.frame(lo$`L65-291`$MEDICATION)%>%
  rename_col_by_position(1, drug)
l65292<-as.data.frame(lo$`L65-292`$MEDICATION)%>%
  rename_col_by_position(1, drug)
n24325<-as.data.frame(lo$`N24-325`$MEDICATION)%>%
  rename_col_by_position(1, drug)

dif131<-anti_join(normal,j02131)
dif291<-anti_join(normal,l65291)
dif325<-anti_join(normal,n24325)
```

current medication 
```{r current meds}
setwd("C:/Users/SamBr/Documents/pgx/myDNA_PATIENT_DRUGS")
getwd()
files3 <- list.files("C:/Users/SamBr/Documents/pgx/myDNA_PATIENT_DRUGS")
temp3 <- lapply(files3, fread, sep=",")
data3 <- as.data.frame(rbindlist(temp3, use.names = TRUE))%>%
  mutate_if(is.character, str_trim)






```